---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# R/`intermed`

[![Travis-CI Build Status](https://travis-ci.org/benkeser/intermed.svg?branch=master)](https://travis-ci.org/benkeser/intermed)
[![AppVeyor Build  Status](https://ci.appveyor.com/api/projects/
tus/github/benkeser/intermed?branch=master&svg=true)](https://ci.appveyor.com/project/benkeser/intermed)
[![Coverage Status](https://img.shields.io/codecov/c/github/benkeser/intermed/master.svg)](https://codecov.io/github/benkeser/intermed?branch=master)
[![CRAN](http://www.r-pkg.org/badges/version/intermed)](http://www.r-pkg.org/pkg/intermed)
[![CRAN downloads](https://cranlogs.r-pkg.org/badges/intermed)](https://CRAN.R-project.org/package=intermed)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![MIT license](http://img.shields.io/badge/license-MIT-brightgreen.svg)](http://opensource.org/licenses/MIT)
[![DOI](https://zenodo.org/badge/75324341.svg)](https://zenodo.org/badge/latestdoi/75324341)

> Nonparametric estimators of mediation effects with multiple mediators

__Author:__ [David Benkeser](https://www.benkeserstatistics.com/)

---

## Description

`intermed` is an R package that computes interventional mediation effects for two
mediators, as introduced in...

---

## Installation

Install the current stable release from
[CRAN](https://cran.r-project.org/) via

```{r cran-installation, eval = FALSE}
install.packages("intermed")
```

A developmental release may be installed from GitHub via
[`devtools`](https://www.rstudio.com/products/rpackages/devtools/) with:

```{r gh-installation, eval = FALSE}
devtools::install_github("benkeser/intermed")
```

---

## Usage

Coming soon... 

---

## Issues

If you encounter any bugs or have any specific feature requests, please [file an
issue](https://github.com/benkeser/intermed/issues).

---

## Citation

After using the `intermed` R package, please cite the following:

    @Manual{intermedpackage,
      title = {intermed: Nonparametric Inference on Interventional Mediation Effects},
      author = {David Benkeser},
      note = {R package version 1.0.0},
      doi = {10.5281/zenodo.844836}
    }

---

## License

&copy; 2021 [David C. Benkeser](http://www.benkeserstatistics.com)

The contents of this repository are distributed under the MIT license. See
below for details:
```
The MIT License (MIT)

Copyright (c) 2021- David C. Benkeser

Permission is hereby granted, free of charge, to any person obtaining a copy
of this software and associated documentation files (the "Software"), to deal
in the Software without restriction, including without limitation the rights
to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
copies of the Software, and to permit persons to whom the Software is
furnished to do so, subject to the following conditions:

The above copyright notice and this permission notice shall be included in all
copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
SOFTWARE.
```